Distributed Nonlinear Feedback Design with Separable Control-Contraction Metrics

### 2017-01-10 R0V0.tex
item I.5

\mypara The drawback of methods such as CCMs, $H_\infty$ optimization and LQR is that, when the system under consideration has many states (large scale), it does not scale well. This is due to the fact that the stability verification of a system with $n$ states may require a function with $n^2$ terms (see \cite{Rantzer2015} for the case of linear systems and Lyapunov functions).

>>>>

\mypara The drawback of methods such as CCMs, $H_\infty$ optimization and LQR is that, when the system under consideration has many states (large scale), it does not scale well. This is due to the fact that the stability verification of a linear system with $n$ states may require a function with $n^2$ terms (see \cite{Rantzer2015} for the case of linear systems and Lyapunov functions). In general, the case is worse, for nonlinear systems.
